---
title: "01-2_Problem-Set"
author: 
date: '`r Sys.Date()`'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Complete the following, replacing the *italic* text. Knit this document to a pdf, **double check the pdf document for errors**, and submit this to the Week 01 Problem Set assignment on Canvas. 

## Problem 1 - Help

Choose any function (type in your favorite letter and press `tab` to complete the function name) and open its documentation in the **Help** pane. What function did you choose? 
*answer here*

Copy the **Usage** section of your chosen function into a code chunk below.  
*answer here*

## Problem 2 - Markdown intros

Find an introduction to Rmarkdown or Quarto that resonates with you somewhere on the internet. 

What do you like about this introductory material?

## Problem 3 - Examples

Find an example of a cool-to-you website that was made with RMarkdown or Quarto (not one I showed you in class). Paste the URL link below. 

*<link>*

What do you think is cool about this website? What do you like about how it is formatted? Insert a screenshot of something you like about the website into this document. 
 
*answer here, including screenshot*

## Problem 4 - Resume/CV

(Adapted from <https://r4ds.hadley.nz/quarto>) Practice what you’ve learned by creating a brief markdown resume (or *Curriculum Vitae*, CV). The title should be your name, and you should include headings for (at least) education or employment. Each of the sections should include a bullet list of job responsibilities, or relevant classes. Highlight the years in bold.

*CV here*

## Problem 5 - Errors

The first code block below has an error in it. Change the settings of the code block to print the error and continue running the second code block, which doesn't have an error.

```{r}
print("Hello world)
```

```{r}
print("Hello world")
```